\Title

### 2020-03-10 manuscript/manuscript.tex
Add citation to Harmonica v0.1.0 (#36)
Add BibTeX entry for Harmonica v0.1.0 and cite it on manuscript.

The subsequent comparisons between strategies for interpolating data through
equivalent sources are carried out by the equivalent sources implementation in
Harmonica \citep{harmonica}.

>>>>

The subsequent comparisons between strategies for interpolating data through
equivalent sources are carried out by the equivalent sources implementation in
Harmonica (v0.1.0) \citep{uieda2020}.
